An Evaluation of RDF Constraint Types to Validate Metadata on Person-Level and Aggregated Data

### 2015-03-12 paper/paper7/paper7-evaluation.tex
evaluation

>>>>

\section{Disco}

\begin{itemize}
	\item DwB Resource Discovery Portal
	\begin{itemize}
	  \item Metadata records for each study are available on the study landing pages.
		\item \url{http://dwb-dev.nsd.uib.no/portal/#/study/http://portal.dwbproject.org/resource/Study/de.gesis/zacat/ZA5597/en}
    \item Search interface: \url{http://dwb-dev.nsd.uib.no/portal/#/search?q=smoking&p=1&s=score&d=desc&f=text}
	\end{itemize}
\end{itemize}
